---
title: "Week 3 Assignment"
date: "11/8/2021"
output: html_document
---Developing Data Products
Week 3 Assignment
========================================================
author: Krystle Sawyer
date: `r date()`
autosize: true

Assignment
========================================================

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. 

## Rubric

1.Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?

2.Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?

Slide With Code
========================================================

```{r}
summary(iris)
```

Slide With Plot
========================================================

```{r, echo=FALSE}
library(plotly)
library(webshot)
plot_ly(iris, y = ~Petal.Length, color = ~Species, type = "box")
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plotly)
```
Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. 

## Rubric

1.Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?

2.Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?

```{r cars}
summary(cars)
```

```{r, eval=FALSE}
plot_ly(iris, y = ~Petal.Length, color = ~Species, type = "box")
```
